Flat-histogram method comparison on the 2D Ising model

### 2020-07-02 ising/ising-body.tex
edit intro paragraphs

% optimized ensemble paragraph
A problem that flat-histogram methods face is that the convergence rate is
impacted by energy barriers and bottleneck which make traversing the phase
space difficult. Nadler \emph{et al.} and Trebst \emph{et al.} systematically
examined optimized ensembles due to performance issues flat-histogram methods
faced when confronted with hidden energy barriers~\cite{nadler2007generalized,
nadler2007dynamics, trebst2004optimizing}. The goal of these methods is to make
the statistical errors uniform such that low energy errors do not dominate over
high energy errors.

@@

Parallel tempering (replica exchange) is a powerful method for overcoming
energy barriers~\cite{geyer1995annealing, hukushima1996exchange,
hansmann1997parallel}. The method works by breaking the simulation up into many
`replicas' and simulating in parallel. At certain times, neighboring replicas
are allowed to exchange which enables the phase space to be more evenly
explored.

Flat-histogram methods, such as Replica exchange Wang-Landau
(REWL)~\cite{vogel2013rewl,perera2016magnetic}, have been proposed that combine
histogram and replica exchange methods. This demonstrates that flat-histogram
methods can be extended to non-flat-histogram methods.

>>>>

% optimized ensemble paragraph
Another challenge that flat-histogram methods face is that the convergence rate is
impacted by energy barriers and bottleneck which can make traversing the phase
space difficult. Nadler \emph{et al.} and Trebst \emph{et al.} systematically
examined optimized ensembles to address performance issues flat-histogram methods
face when confronted with hidden energy barriers~\cite{nadler2007generalized,
nadler2007dynamics, trebst2004optimizing}.
The approach involves using an ensemble that does \emph{not} result in a
flat histogram, but instead optimizes the rate of diffusion between low
energy and high energy states.
The goal of these methods is to make the statistical errors uniform.
%
Optimized ensemble methods typically begin by using a flat-histogram method
to get a first approximation for the weights, which means that any of the
methods
tested in this work could be used as a starting point for an optimized
ensemble simulation.

@@

An approach to parallelizing flat-histogram Monte Carlo methods is
the replica-exchange approach, which was pioneered by parallel tempering
algorithms~\cite{geyer1995annealing, hukushima1996exchange,
hansmann1997parallel}.  Vogel \emph{et al.} adapted this approach to develop
the Replica Exchange Wang-Landau (REWL)~\cite{vogel2013rewl} approach.  This
approach for parallelization is sufficiently simple and general that it could
equally be applied to any of the methods explored in this paper.
